Quality-of-Content (QoC)-Based Wireless Video Transmissions: A Joint Source Coding and APP-FEC Rate Allocation Scheme for Human Detections in Mobile Surveillance Networks

### 2015-07-26 draft.tex
More details added in the simulation section
Revised equation of the APP-FEC correction rate for non-ideal codes

\section{APP-FEC and Block Correction Rate}
APP-FEC can provide reliable end-to-end streaming applications with packet level protection \cite{LuSW08}. Suppose a source block with $k$ packets is encoded into an APP-FEC block consisting $n \left(n\geq k\right)$ packets by adding $n-k$ redundant packets, an ideal APP-FEC decoder can reconstruct the original $k$ source packets from any $k$ out of $n$ received packets \cite{LuSW08} with correction capability $t=n-k$. The Reed-Solomon (RS) code, which operates on non-binary symbols, is a well-known APP-FEC scheme with ideal correction capability. However, the block size of RS code is constrained by the symbol size, which limits the flexibility of parameter selections in practice. For instance, considering the most commonly used RS code with $8$ bits per symbol, the total number of packets in an APP-FEC block is constrained by $255$, i.e., $k\leq n \leq 255$. Furthermore, the non-binary operations of the RS code cause high computational complexity in software \cite{LuSW08}. Such drawbacks make the RS code unattractive to high definition (HD) video streaming applications. With the development of APP-FEC, more practical schemes have been introduced. One of the attractive APP-FEC solutions for HD video streaming services is the Raptor code \cite{Shok06}, which has flexible parameters selection and linear decoding cost. Unlike the RS code, the correction capability of a Raptor code is unideal, given by $t=n\left(1+\epsilon\right)k$, where $\epsilon$ is reception overhead efficiency. Nevertheless, the reception overhead efficiency of standardized Raptor code is very low and close to ideal correction capability \cite{LuSW08}. In this paper, the APP-FEC scheme with ideal correction capabiity is assumed for simplicity.

@@

\section{Simulation Results}
In this section, the proposed QoC-driven rate allocation scheme is evaluated by plenty of simulations. In total four video clips are used to compete for the limited wireless resources: two videos ``LINTHESCHER" and ``LOEWENPLATZ" from the ETHZ data set \cite{ELSG08} and two videos recorded in the UW campus. Table \ref{Table: video} summarizes the resolutions and human densities of the four videos. HEVC (X265 implementation) \cite{X265} is used as the video encoder. The frame rate and GoP are set as $25$ fps and $16$ respectively for all the videos. The encoding pattern in each GoP block is one I-frame followed by $15$ P-frames. $25$ GoPs ($400$ frames) are simulated for each video. Figure \ref{fig:sampleFrames} shows the sample video frames of the four videos.

@@

Table \ref{Table: schemes} summarizes the proposed and other rate allocation schemes in the control group. We compare the proposed scheme with other three schemes. The first one is driven by video distortion measured by the mean-squared-error (MSE). We adopte a rate-distortion model in \cite{HOSC10} as:
\begin{equation}
d_m\left(r\right)=c_m^{\left(3\right)}r^{c_m^{\left(4\right)}},
\end{equation}
where $d_m\left(r\right)$ is the distortion in terms of MSE for the mobile node $m$. $c_m^{\left(3\right)}$ and $c_m^{\left(4\right)}$ are two parameters to be determined by curve-fitting. The MSE-driven rate allocation problem is expressed as:
\begin{equation}
\begin{array}{rl}
\min_{\mathbf{\tilde{k}},\mathbf{\tilde{n}}} &\sum_{m=1}^{M}d_m\left(\frac{\tilde{k}^2_m \cdot S}{T^{\left(\text{GoP}\right)}}\right) \\
\text{subject to} & \sum\limits_{m=1}^{M}\tilde{n}^2_m\leq \frac{R^{\left(\text{T}\right)}T^{\left(\text{GoP}\right)}}{S}\\
& \tilde{k}_m \geq \sqrt{\frac{R^{\left(\min\right)}T^{\left(\text{GoP}\right)}}{S}}, \forall m, \\
& \tilde{n}_m \geq \tilde{k}_m, \forall m \\
& \log\Phi\left(\frac{\tilde{n}_m\left(1-p_m\right)-\frac{\tilde{k}_m^2}{\tilde{n}_m}}{\sqrt{p_m\left(1-p_m\right)}}\right) \geq \log(P^{\left(\text{req}\right)}), \forall m,
\end{array}
\end{equation}
where $P^{\left(\text{req}\right)}$ is a pre-defined BCR requirement, which is set as $0.99$ \cite{WSHZ13} in this paper. The minimum data rate requirement $R^{\left(\min\right)}$ in our proposed scheme and the MSE-driven rate allocation scheme are both set as $200$ Kbps.

>>>>

\section{APP-FEC and Block Correction Rate}
APP-FEC can provide reliable end-to-end streaming applications with packet level protection \cite{LuSW08}. Suppose a source block with $k$ packets is encoded into an APP-FEC block consisting $n \left(n\geq k\right)$ packets by adding $n-k$ redundant packets, an ideal APP-FEC decoder can reconstruct the original $k$ source packets from any $k$ out of $n$ received packets \cite{LuSW08} with correction capability $t=n-k$. The Reed-Solomon (RS) code, which operates on non-binary symbols, is a well-known APP-FEC scheme with ideal correction capability. However, the block size of RS code is constrained by the symbol size, which limits the flexibility of parameter selections in practice. For instance, considering the most commonly used RS code with $8$ bits per symbol, the total number of packets in an APP-FEC block is constrained by $255$, i.e., $k\leq n \leq 255$. Furthermore, the non-binary operations of the RS code cause high computational complexity in software \cite{LuSW08}. Such drawbacks make the RS code unattractive to high definition (HD) video streaming applications. With the development of APP-FEC, more practical schemes have been introduced. One of the attractive APP-FEC solutions for HD video streaming services is the Raptor code \cite{Shok06}, which has flexible parameters selection and linear decoding cost. Unlike the RS code, the correction capability of a Raptor code is unideal, given by $t=n-\left(1+\epsilon\right)k$, where $\epsilon$ is reception overhead efficiency. Nevertheless, the reception overhead efficiency of standardized Raptor code is very low and close to ideal correction capability \cite{LuSW08}. In this paper, the APP-FEC scheme with ideal correction capabiity is assumed for simplicity.

@@

\section{Simulation Results}
In this section, the proposed QoC-driven rate allocation scheme is evaluated by plenty of simulations. In total four video clips are used to compete for the limited wireless resources: two videos ``LINTHESCHER" and ``LOEWENPLATZ" from the ETHZ data set \cite{ELSG08} and two videos recorded in the UW campus. Table \ref{Table: video} summarizes the resolutions and human densities of the four videos. HEVC (X265 implementation) \cite{X265} is used as the video encoder. The frame rate and GoP are set as $25$ fps and $16$ respectively for all the videos. Hence the GoP period ($T^{\left(\text{GoP}\right)}$) is $0.64$ s. The encoding pattern in each GoP block is one I-frame followed by $15$ P-frames. $25$ GoPs ($400$ frames) are simulated for each video. Figure \ref{fig:sampleFrames} shows the sample video frames of the four videos. The packet size ($S$) is set as $600$ bytes.

@@

Table \ref{Table: schemes} summarizes the proposed and other rate allocation schemes in the control group. We compare the proposed scheme with other three schemes. The first one is driven by video distortion measured by the mean-squared-error (MSE). We adopte a rate-distortion model in \cite{HOSC10} as:
\begin{equation}
d_m\left(r\right)=c_m^{\left(3\right)}r^{c_m^{\left(4\right)}},
\end{equation}
where $d_m\left(r\right)$ is the distortion in terms of MSE for the mobile node $m$. $c_m^{\left(3\right)}$ and $c_m^{\left(4\right)}$ are two parameters to be determined by curve-fitting. The MSE-driven rate allocation problem is expressed as:
\begin{equation}
\begin{array}{rl}
\min_{\mathbf{\tilde{k}},\mathbf{\tilde{n}}} &\sum_{m=1}^{M}d_m\left(\frac{\tilde{k}^2_m \cdot S}{T^{\left(\text{GoP}\right)}}\right) \\
\text{subject to} & \sum\limits_{m=1}^{M}\tilde{n}^2_m\leq \frac{R^{\left(\text{T}\right)}T^{\left(\text{GoP}\right)}}{S}\\
& \tilde{k}_m \geq \sqrt{\frac{R^{\left(\min\right)}T^{\left(\text{GoP}\right)}}{S}}, \forall m, \\
& \tilde{n}_m \geq \tilde{k}_m, \forall m \\
& \log\Phi\left(\frac{\tilde{n}_m\left(1-p_m\right)-\frac{\tilde{k}_m^2}{\tilde{n}_m}}{\sqrt{p_m\left(1-p_m\right)}}\right) \geq \log(P^{\left(\text{req}\right)}), \forall m,
\end{array}
\end{equation}
where $P^{\left(\text{req}\right)}$ is a pre-defined BCR requirement, which is set as $0.99$ \cite{WSHZ13} in this paper. The MSE-driven rate allocation problem is also convex (similar proof as Eq. \eqref{eq:finalProblem}) and can be solved by the CVX \cite{CVX}. The minimum data rate requirement $R^{\left(\min\right)}$ in our proposed scheme and the MSE-driven rate allocation scheme are both set as $200$ Kbps.
